Getting start

### 2020-12-01 inst/gitbook/01_getting_started.Rmd
typos + minors

```{r}
set.seed(1)
## Setting the simulation parameters
extinction_02 <- list(extinction = 0.4)
living_20     <- list(max.living = 20)
BM_trait      <- make.traits()
set.seed(4242)
## Simulate disparity and diversity
default_data <- dads(bd.params = extinction_02,
                     stop.rule = living_20,
                     traits    = BM_trait,
                     modifiers = default_modifiers)
default_data
```

>>>>

```{r}
## Setting the simulation parameters
extinction_02 <- list(extinction = 0.4)
living_20     <- list(max.living = 20)
BM_trait      <- make.traits()
set.seed(4242)
## Simulate disparity and diversity
default_data <- dads(bd.params = extinction_02,
                     stop.rule = living_20,
                     traits    = BM_trait,
                     modifiers = default_modifiers)
default_data
```
